Towards an Automated Sportscasting System for Chess

### 2011-05-18 paper/paper.tex
Submitted paper.
Paper debugged

However, we identified some shortcomings of the AMBL system. First, it relies on experts to provide arguments as to why a certain position exemplifies (or doesn’t) a particular positional feature. While this is an improvement from defining a classification rule manually, it is infeasible to repeat this procedure multiple times. Second, the arguments that the experts are allowed to provide rely on a preset list of features.

@@

\begin{table*}[p]
\centering
\vspace{-0.7cm}
\begin{tabular}{lp{0.6\textwidth}}
\hline
\textbf{Name} & \textbf{Description} \\ \hline
\tt{attackPossible} & The current player has opportunity to attack. \\
\tt{backrankWeakness} & There exists a future checkmate by a rook or queen on the edges of the board. \\
\tt{bishopPair} & There exists a decisive strategic advantage for the player with two bishops. \\
\tt{clearance} & There exists a maneuver to break the pawn structure. \\ 
\tt{closure} & There exists a maneuver to fix the pawn structure. \\
\tt{decoy} & There exists a maneuver to distract a crucial piece. \\
\tt{defensePressure} & There exists a maneuver to break the opposing King’s defense. \\
\tt{deflection} & There exists a maneuver to deflect an attack.  \\ 
\tt{discoveredAttack} & There exists a maneuver to allow for a discovered attack (an attack that was blocked by a friendly piece.) \\
\tt{doubleAttack} & There exists a move that simultaneously attacks at least two crucial squares. \\
\tt{drawCombinationsStalemate} & There exists a combination that allows for decisive material advantage or immediate checkmate. \\
\tt{enclosedKings} & There exists a maneuver to trap the opposing King. \\
\tt{freeingBlockingSquares} & There exists a move to free a crucial square. \\
\tt{goodEndgameChances} & There exists a move to allow for a favorable endgame. \\
\tt{inBetweenMove} & There exists an interrupting move that allows for decisive material advantage of immediate checkmate. \\ 
\tt{interference} & There exists a maneuver to block a crucial piece. \\ 
\tt{interruption} & There exists a maneuver that interrupts the opponent’s tactics. \\
\tt{kingInCenter} & There exists a decisive strategic advantage for the player with the King in the center of the board. \\
\tt{kingToBadSquares} & There exists a combination that forces the opposing King to move to a bad square. \\
\tt{longDiagonals} & There exists a strategic advantage for the player that controls squares on the long diagonal. \\
\tt{matingAttack} & There exists a decisive mating attack. \\
\tt{openingClosingDiagonals} & There exists a maneuver to clear a diagonal. \\
\tt{openingClosingFiles} & There exists a maneuver to clear a file. \\
\tt{overload} & There exists a combination that makes a defending piece defend too many squares at once. \\
\tt{passedPawn} & There exists a combination that allows for a passed pawn (a pawn with no opposing pawns in front of it.) \\
\tt{pawnPromotion} & There exists a combination that allows for a pawn promotion. \\
\tt{perpetualCheck} & There exists a combination that forces a perpetual check/draw. \\
\tt{pin} & There exists a combination that allows for a pin. \\
\tt{pullingPiecesToBadSquares} & There exists a combination that forces an opposing piece to move to a bad square. \\
\tt{queenCapture} & There exists a combination to capture the opposing Queen. \\
\tt{quietMates} & There exists a quiet move (one that looks inconsequential on the surface) leading to mate. \\
\tt{removalOfDefence} & There exists a maneuver to remove an opponent’s defender. \\
\tt{unpinning} & There exists a maneuver to unpin a piece. \\
\tt{wrongBishop} & The opponent’s only bishop is limited in use because of the pawn structure of the game. \\ \hline
\end{tabular}
\caption{List of high-level themes we attempt to automatically identify, along with explanations}
\label{table:themes}
\end{table*}

>>>>

However, we identified some shortcomings of the AMBL system. First, it relies on experts to provide arguments as to why a certain position exemplifies (or doesn't) a particular positional feature. While this is an improvement from defining a classification rule manually, it is infeasible to repeat this procedure multiple times. Second, the arguments that the experts are allowed to provide rely on a preset list of features.

@@

\begin{table*}[p]
\centering
\vspace{-0.7cm}
\begin{tabular}{lp{0.6\textwidth}}
\hline
\textbf{Name} & \textbf{Description} \\ \hline
\tt{attackPossible} & The current player has opportunity to attack. \\
\tt{backrankWeakness} & There exists a future checkmate by a rook or queen on the edges of the board. \\
\tt{bishopPair} & There exists a decisive advantage for the player with 2 bishops. \\
\tt{clearance} & There exists a maneuver to break the pawn structure. \\ 
\tt{closure} & There exists a maneuver to fix the pawn structure. \\
\tt{decoy} & There exists a maneuver to distract a crucial piece. \\
\tt{defensePressure} & There exists a maneuver to break the opposing King's defense. \\
\tt{deflection} & There exists a maneuver to deflect an attack.  \\ 
\tt{discoveredAttack} & There exists a maneuver to allow for a discovered attack (an attack that was blocked by a friendly piece.) \\
\tt{doubleAttack} & There exists a move that simultaneously attacks two squares. \\
\tt{drawCombinationsStalemate} & There exists a combination that allows for decisive material advantage or immediate checkmate. \\
\tt{enclosedKings} & There exists a maneuver to trap the opposing King. \\
\tt{freeingBlockingSquares} & There exists a move to free a crucial square. \\
\tt{goodEndgameChances} & There exists a move to allow for a favorable endgame. \\
\tt{inBetweenMove} & There exists an interrupting move that allows for decisive material advantage of immediate checkmate. \\ 
\tt{interference} & There exists a maneuver to block a crucial piece. \\ 
\tt{interruption} & There exists a maneuver that interrupts the opponent’s tactics. \\
\tt{kingInCenter} & There exists a decisive strategic advantage for the player with the King in the center of the board. \\
\tt{kingToBadSquares} & There exists a combination that forces the opposing King to move to a bad square. \\
\tt{longDiagonals} & There exists a strategic advantage for the player that controls squares on the long diagonal. \\
\tt{matingAttack} & There exists a decisive mating attack. \\
\tt{openingClosingDiagonals} & There exists a maneuver to clear a diagonal. \\
\tt{openingClosingFiles} & There exists a maneuver to clear a file. \\
\tt{overload} & There exists a combination that makes a defending piece defend too many squares at once. \\
\tt{passedPawn} & There exists a combination that allows for a passed pawn (a pawn with no opposing pawns in front of it.) \\
\tt{pawnPromotion} & There exists a combination that allows for a pawn promotion. \\
\tt{perpetualCheck} & There exists a combination that forces a perpetual check/draw. \\
\tt{pin} & There exists a combination that allows for a pin. \\
\tt{pullingPiecesToBadSquares} & There exists a combination that forces an opposing piece to move to a bad square. \\
\tt{queenCapture} & There exists a combination to capture the opposing Queen. \\
\tt{quietMates} & There exists a quiet move (one that looks inconsequential on the surface) leading to mate. \\
\tt{removalOfDefence} & There exists a maneuver to remove an opponent’s defender. \\
\tt{unpinning} & There exists a maneuver to unpin a piece. \\
\tt{wrongBishop} & The opponent’s only bishop is limited in use because of the pawn structure of the game. \\ \hline
\end{tabular}
\caption{List of high-level themes we attempt to automatically identify, along with explanations}
\label{table:themes}
\end{table*}
